---
title: "Thesis Analysis"
author: "RS"
date: "2023-04-17"
output:
  html_document:
    theme: flatly
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

The objective of this R markdown document is to carry out multiple tasks such as uploading the JSON files, data cleaning, variable renaming, and conducting the analysis.

# Legend
```{r, error=FALSE, warning = FALSE, message = FALSE}
# 1. rt.x: shows the time that they spend on each org.page in milliseconds

# 2. trial index: In total we have 14 trials the participants go through during the questionnaire. 

# 3. trial condition: 0-4 with 4 being most equal in female and non-whites (10 employees)

# 4. nNonWhiteTrial: absolute number of non-White employees in this trial condition

# 5. nWhiteTrial: absolute number of White employees in this trial condition

# 6. nNonWhiteFemaleTrial: absolute number of non-White female employees in this trial condition

# 7. nNonWhiteMaleTrial: absolute number of non-White male employees in this trial condition

# 8. nWhiteFemaleTrial: absolute number of White female employees in this trial condition

# 9. nWhiteMaleTrial: absolute number of White male employees in this trial condition

# 10. DV: fairness, teamwork, work in team, distrust in organization

```

# Data Cleaning 
```{r, error=FALSE, warning = FALSE, message = FALSE}
######################### loading packages #########################

library(jsonlite)
library(dplyr)
library(tidyverse)
library(ggplot2)  
library(ggforce)
library(sjPlot)
library(lme4)
library(lmerTest)
library(interactions)
library(ggpubr)
library(texreg)
library(reghelper)
library(tidyr)


######################## uploading JSON files #######################

# uploading every json file and creating one big file 
setwd("C:/Users/ramat/Desktop/data_2023")

# read all the files with jason ending
filenames <- list.files(pattern="*.json", recursive = T)
files <- lapply (filenames, fromJSON)
isCompleted <- lapply(files, nrow)

# we have 14 trials in total
completedData <- files[isCompleted == 14 ]

# every trial is in all_data combined
all_data <- do.call("bind_rows", completedData)
raw_data <- all_data


####################### correcting duplicates #######################

# due to duplicates in the data selecting 
values_subject<-names(table(all_data$subject)) #extract labels from part

Data_filter<-c() #empty object

for (i in c(1:length(values_subject)))
{
 data_sub<-all_data[all_data$subject==values_subject[i],] #subset data
 data_sub<-data_sub[c(1:14),]  #delete everything but the first 14 trials
 Data_filter[[i]]<-data_sub
}

raw_data<-do.call(rbind,Data_filter )  #merge again


######################## combining 14 trials ########################

# trial index 0 = attention check
atten_trial <- 0

atten_data <- raw_data[raw_data$trial_index == atten_trial, ]
atten_data <- atten_data %>% unnest(response) %>% unnest()
names(atten_data)[names(atten_data) == "response"] <- "attention_check"

#trial index 1 = prolific ID
prolific_trial <- 1
prolific_data <- raw_data[raw_data$trial_index == prolific_trial, ]
prolific_data <- prolific_data %>% unnest(response)
names(prolific_data)[names(prolific_data) == "response"] <- "prolific_id"

#trial index 2 = trial consent 
#trial index 3 = trial 
#trial index 4 = continue after trial

#trial index 5-9 = organizations
org_trials <- c(5,6,7,8,9)
org_data <- raw_data[raw_data$trial_index %in% org_trials, ]
org_data <- org_data %>% unnest(response)  
org_data <- org_data %>% pivot_wider(names_from = name, values_from = value) %>% unnest()

#trial index 10 = Moderator SDO and belief in justice world
moderator_trials <- c(10)
mod_data <- raw_data[raw_data$trial_index %in% moderator_trials, ]
mod_data <- mod_data %>% unnest(response) %>% pivot_wider(names_from = name, values_from = value) %>% unnest()

#trial index 12 = follow up trial
followup_trials <- c(12)

followup_data <- raw_data[raw_data$trial_index %in% followup_trials, ]
followup_data <- followup_data %>% unnest(response) %>% unnest()
names(followup_data)[names(followup_data) == "response"] <- "followup_response"

#trial index 11 = demographics information
demographics_trials <- c(11)
demo_data <- raw_data[raw_data$trial_index %in% demographics_trials, ]
demo_data <- demo_data %>% unnest(response)

demo_data_wo_ethnic <- demo_data[demo_data$name != "ethnic[]", ]  %>% pivot_wider(names_from = name, values_from = value)
demo_data_ethnic <- demo_data[demo_data$name == "ethnic[]", ]
demo_data_ethnic <- demo_data_ethnic %>% mutate(ethnic = c( value))
demo_data <- inner_join(demo_data_ethnic[, c("rt", "subject", "ethnic")], demo_data_wo_ethnic, by="subject") %>% unique() %>% unnest()


############# removing mistake due to double responses ##############
demo_data<-demo_data[-c(18,35,57,58,59,60,61,71,80,81,86,89,137,153,172,179,181,221),]


###################### Socio demographic data #######################

demo_cols <- c("ethnic", "age", "children", "economic", "edu", "employment", "gender", "gender_description", "income", "ladder", "marital", "social")


############### Join all the variables into one excel ###############

data <- inner_join(org_data, mod_data[, c("rt", "subject", "A1", "A2", "A3", "A4", "A5", "A6", "A7", "A8", "B1", "B2", "B3", "B4", "B5", "B6")], by = "subject") 

data <- inner_join(data, demo_data[, c("subject", demo_cols)], by = "subject") 
data <- inner_join(data, followup_data[, c("subject", "followup_response")], by = "subject") 
data <- inner_join(data,atten_data[, c("subject", "attention_check")], by = "subject")


################# Creating excel to check manually ##################
#write.csv(data, "C:/Users/ramat/Desktop/data_2023/cleaned_data_test.csv")


##################### Cleaning the environment ######################
remove(mod_data,org_data, prolific_data,raw_data,all_data, atten_data,completedData,demo_data, demo_data_ethnic, demo_data_wo_ethnic, files, followup_data, isCompleted, data_sub, Data_filter)


################# dropping failed attention checks ##################

#only put 1 into new subset
data1<- subset(data, attention_check == "R" | attention_check == "r")

remove(data)


############# dropping attention checks more than 3SD ##############

values_subject<-names(table(data1$subject)) #extract labels from part

Outlier<-c() #empty object


for (i in c(1:length(values_subject)))
{
  
data_sub<-data1[data1$subject==values_subject[i],] #subset data
outlier<-ifelse(data_sub$rt.x>(mean(data1$rt.x)+(3*sd(data1$rt.x))), rep(TRUE,length(data_sub$rt.x)),rep(FALSE,length(data_sub$rt.x)))
outlier<-ifelse(outlier==TRUE,values_subject[i],NA)
Outlier[[i]]<-outlier
 #delete everything but the first 14 trials
}


Outlier<-do.call(rbind,Outlier )  #merge again


Outlier_ID<-c(Outlier[,1],Outlier[,2],Outlier[,3],Outlier[,4],Outlier[,5])
Outlier_ID<-Outlier_ID[is.na(Outlier_ID)==FALSE]


###filter data 1 outlier id
data2<-subset(data1, !(data1$subject %in% Outlier_ID))


################# removing unnecessary columns ##################

data2<-(data2%>% select(-internal_node_id, -browser_name, -browser_type, -interaction, -windowWidth, - windowHeight, -stimulus, -trial_type, -whiteNonwhiteRatio,-time_elapsed, -completed, -rt.y,))

remove(data_sub)
remove(Outlier)
remove(data1)

###################### renaming variables #######################

# DV:Fairness, Team Work, Work in team, Distrust
names(data2)[names(data2) == "perception1"] <- "fairness"
names(data2)[names(data2) == "perception2"] <- "team_work"
names(data2)[names(data2) == "perception3"] <- "work_in_team"
names(data2)[names(data2) == "perception4"] <- "distrust"

# DV scale example
#data2$fairness[data2$fariness == 1] <- "Strongly disagree"
#data2$fairness[data2$fairness == 2] <- "Disagree"
#data2$fairness[data2$fairness == 3] <- "Neither Agree or Disagree"
#data2$fairness[data2$fairness == 4] <- "Agree"
#data2$fairness[data2$fairness == 5] <- "Strongly Agree"

#DV questions:
# People on this team have equal opportunities to advance. near 1=no its unfair near 5 = yes fair
# People on this team work together well
# I would like to work in this team
# I trust the organization's leadership to make good decisions

# Moderator 1: SDO
names(data2)[names(data2) == "A1"] <- "s1_earn_reward"
names(data2)[names(data2) == "A2"] <- "s2_inferior"
names(data2)[names(data2) == "A3"] <- "s3_group_dominat"
names(data2)[names(data2) == "A4"] <- "s4_bottom_deserve"
names(data2)[names(data2) == "A5"] <- "s5_group_equality"
names(data2)[names(data2) == "A6"] <- "s6_group_equal_unjust"
names(data2)[names(data2) == "A7"] <- "s7_act_equalize"
names(data2)[names(data2) == "A8"] <- "s8_succeed_equal"

data2$SDO <- (((as.numeric(data2$s1_earn_reward))+(as.numeric(data2$s2_inferior))+(as.numeric(data2$s3_group_dominat))+(as.numeric(data2$s4_bottom_deserve))+(as.numeric(data2$s5_group_equality))+(as.numeric(data2$s6_group_equal_unjust))+(as.numeric(data2$s7_act_equalize))+(as.numeric(data2$s8_succeed_equal))))/8

#SDO scale example
#data2$s1_earn_reward[data2$s1_earn_reward == 1] <- "Strongly favor"
#data2$s1_earn_reward[data2$s1_earn_reward == 2] <- "Somewhat favor"
#data2$s1_earn_reward[data2$s1_earn_reward == 3] <- "Slightly favor"
#data2$s1_earn_reward[data2$s1_earn_reward == 4] <- "Neutral"
#data2$s1_earn_reward[data2$s1_earn_reward == 5] <- "Slightly oppose"
#data2$s1_earn_reward[data2$s1_earn_reward == 6] <- "Somewhat oppose"
#data2$s1_earn_reward[data2$s1_earn_reward == 7] <- "Strongly oppose"

# Moderator 2: Trial Condition

# Moderator 3: Political Orientation:
data2$PoliticalOrientation <- ((as.numeric(data2$social))+(as.numeric(data2$economic)))/2
#Political orientation - social issues - legend
#data2$economic[data2$economic == 1] <- "Conservative"
#data2$economic[data2$economic == 2] <- "Liberal"
#data2$economic[data2$economic == 3] <- "Moderate"
#data2$economic[data2$economic == 4] <- "Slightly conservative"
#data2$economic[data2$economic == 5] <- "Slightly liberal"
#data2$economic[data2$economic == 6] <- "Very conservative"
#data2$economic[data2$economic == 7] <- "Very liberal"

#Political orientation - economic issues - legend
#data2$social[data2$social == 1] <- "Conservative"
#data2$social[data2$social == 2] <- "Liberal"
#data2$social[data2$social == 3] <- "Moderate"
#data2$social[data2$social == 4] <- "Slightly conservative"
#data2$social[data2$social == 5] <- "Slightly liberal"
#data2$social[data2$social == 6] <- "Very conservative"
#data2$social[data2$social == 7] <- "Very liberal"

# Moderator 4: Belief in Justice World
names(data2)[names(data2) == "B1"] <- "b1_just_world"
names(data2)[names(data2) == "B2"] <- "b2_people_deserve"
names(data2)[names(data2) == "B3"] <- "b3_confident_justice"
names(data2)[names(data2) == "B4"] <- "b4_compensate_injustice"
names(data2)[names(data2) == "B5"] <- "b5_injust_exeception"
names(data2)[names(data2) == "B6"] <- "b6_fair_decision"

data2$BJW <- ((as.numeric(data2$b1_just_world)) + (as.numeric(data2$b2_people_deserve))+ (as.numeric(data2$b3_confident_justice)) + (as.numeric(data2$b4_compensate_injustice))  + (as.numeric(data2$b5_injust_exeception)) + (as.numeric(data2$b6_fair_decision)))/6

#BJW scale 
#data2$b1_just_world[data2$b1_just_world == 1] <- "Strongly disagree"
#data2$b1_just_world[data2$b1_just_world == 2] <- "Disagree"
#data2$b1_just_world[data2$b1_just_world == 3] <- "Slightly disagree"
#data2$b1_just_world[data2$b1_just_world == 4] <- "Slightly Agree"
#data2$b1_just_world[data2$b1_just_world == 5] <- "Agree"
#data2$b1_just_world[data2$b1_just_world == 6] <- "Strongly agree"


# Sociodemographics
#gender
data2$gender[data2$gender == "m"] <- 0
data2$gender[data2$gender == "f"] <- 1
data2$gender[data2$gender == "0"] <- 2

#edu status - legend
#data2$edu[data2$edu == 1] <- "Some high school or less"
#data2$edu[data2$edu == 2] <- "Two year college degree"
#data2$edu[data2$edu == 3] <- "Some college but no degree"
#data2$edu[data2$edu == 4] <- "High school or GED"
#data2$edu[data2$edu == 5] <- "Four year college degree"
#data2$edu[data2$edu == 6] <- "Graduate degree"
#data2$edu[data2$edu == 7] <- "N/A"
#data2$edu[data2$edu == 8] <- "Don't know"

#ethic
data2$ethnic[data2$ethnic == "White"] <- 0
data2$ethnic[data2$ethnic == "Asian"] <- 1
data2$ethnic[data2$ethnic == "Other"] <- 1
data2$ethnic[data2$ethnic == "AI-AN"] <- 1
data2$ethnic[data2$ethnic == "NH-PI"] <- 1
data2$ethnic[data2$ethnic=="Black-AfrAmr"] <- 1

#marital status - legend
#data2$marital[data2$marital == 1] <- "Divorced"
#data2$marital[data2$marital == 2] <- "Married"
#data2$marital[data2$marital == 3] <- "Seperated"
#data2$marital[data2$marital == 4] <- "Widowed"

#Employment - legend
#data2$employment[data2$employment == 1] <- "Full-time"
#data2$employment[data2$employment == 2] <- " Part-time"
#data2$employment[data2$employment == 3] <- "Prefer not to answer"
#data2$employment[data2$employment == 4] <- "Unemployed"

# Income
data2$income[data2$income == 1] <- "$10,000 to $19,999 "
data2$income[data2$income == 2] <- "$100,000 to $124,999"
data2$income[data2$income == 3] <- "$125,000 to $149,999"
data2$income[data2$income == 4] <- "$150,000 to $199,999"
data2$income[data2$income == 5] <- "$20,000 to $29,999"
data2$income[data2$income == 6] <- "$200,000 or more"
data2$income[data2$income == 7] <- "$30,000 to $39,999"
data2$income[data2$income == 8] <- "$40,000 to $49,999"
data2$income[data2$income == 9] <- "$50,000 to $59,999"
data2$income[data2$income == 10] <- "$60,000 to $69,999"
data2$income[data2$income == 11] <- "$70,000 to $79,999"
data2$income[data2$income == 12] <- "$80,000 to $89,999"
data2$income[data2$income == 13] <- "$90,000 to $99,999"
data2$income[data2$income == 14] <- "Less than $10,000"

data2$income[data2$income == "Less than $10,000"] <- 10000
data2$income[data2$income == "$10,000 to $19,999 "] <- 15000
data2$income[data2$income == "$20,000 to $29,999"] <- 25000
data2$income[data2$income == "$30,000 to $39,999"] <- 35000
data2$income[data2$income == "$40,000 to $49,999"] <- 45000
data2$income[data2$income == "$50,000 to $59,999"] <- 55000
data2$income[data2$income == "$60,000 to $69,999"] <- 65000
data2$income[data2$income == "$70,000 to $79,999"] <- 75000
data2$income[data2$income == "$80,000 to $89,999"] <- 85000
data2$income[data2$income == "$90,000 to $99,999"] <- 95000
data2$income[data2$income == "$100,000 to $124,999"] <- 112500
data2$income[data2$income == "$125,000 to $149,999"] <- 137500
data2$income[data2$income == "$150,000 to $199,999"] <- 175000
data2$income[data2$income == "$200,000 or more"] <- 225000

data2$income_log <- log(as.numeric(data2$income))

```
```{r, error=FALSE, warning = FALSE, message = FALSE, results='hide'}
################ prepare variables for analysis #################


data2$whitemen<-ifelse(data2$incomeRatio==1,1,0)
data2$nwhitemen<-ifelse(data2$incomeRatio==2,1,0)
data2$whitefemale<-ifelse(data2$incomeRatio==3,1,0)
data2$nwhitefemale<-ifelse(data2$incomeRatio==4,1,0)
data2$equal<-ifelse(data2$incomeRatio==5,1,0)

#dummy 0 = white male earn more
#dummy 1 = non white male earn more
#dummy 2 = white female earn more
#dummy 3 = non white male earn more
#dummy 4 = equal condition

#transform to DV to numeric values
data2$fairness<- as.numeric(data2$fairness)
data2$team_work<- as.numeric(data2$team_work)
data2$work_in_team<- as.numeric(data2$work_in_team)
data2$distrust<- as.numeric(data2$distrust)
data2$age<-as.numeric(data2$age)
data2$edu<-as.numeric(data2$edu)
data2$children<-as.numeric(data2$children)
data2$income_log<as.numeric(data2$income_log)
data2$ladder<-as.numeric(data2$ladder)

```
# Main Effect Analysis
```{r, error=FALSE, warning = FALSE, message = FALSE, results='hide'}

# Fairness
model_1<-lmer(fairness~ whitemen + nwhitemen+ whitefemale + nwhitefemale + (1|subject), data = data2)
summary(model_1)

# Teamwork
model_2<-lmer(team_work~ whitemen + nwhitemen+ whitefemale + nwhitefemale + (1|subject), data = data2)
summary(model_2)

# Work in team
model_3<-lmer(work_in_team~ whitemen + nwhitemen+ whitefemale + nwhitefemale + (1|subject), data = data2)
summary(model_3)

#distrust
model_4<-lmer(distrust~ whitemen + nwhitemen+ whitefemale + nwhitefemale + (1|subject), data = data2)
summary(model_4)

```

```{r}
h<-htmlreg(l = list(model_1, model_2, model_3, model_4), center = TRUE, stars = c(0.001, 0.01, 0.05), bold = 0.05, caption = 'M1 = Fairness NW (DV), M2 = Team Work NW (DV), M3 = Want to work in team NW (DV), M4 = Distrust NW (DV)', caption.above = TRUE, digits = 3, leading.zero = F)

htmltools::HTML(h)

```
# Main Effects Analysis with control variables
```{r, error=FALSE, warning = FALSE, message = FALSE, results='hide'}

model_5<-lmer(fairness~nwhitefemale + whitemen + nwhitemen+ whitefemale + age + gender + ethnic + edu + marital + children + employment + income_log + ladder + PoliticalOrientation + (1|subject), data = data2)
summary(model_5)

model_6<-lmer(team_work~nwhitefemale + whitemen + nwhitemen+ whitefemale + age + gender + ethnic + edu + marital + children + employment + income_log + ladder + PoliticalOrientation+(1|subject), data = data2)
summary(model_6)

model_7<-lmer(work_in_team~nwhitefemale + whitemen + nwhitemen+ whitefemale + age + gender + ethnic + edu + marital + children + employment + income_log + ladder + PoliticalOrientation+ (1|subject), data = data2)
summary(model_7)

model_8<-lmer(distrust~nwhitefemale + whitemen + nwhitemen+ whitefemale + age + gender + ethnic + edu + marital + children + employment + income_log + ladder + PoliticalOrientation + (1|subject), data = data2)
summary(model_8)

```
```{r}
h<-htmlreg(l = list(model_5, model_6, model_7, model_8), center = TRUE, stars = c(0.001, 0.01, 0.05), bold = 0.05, caption = 'M1 = Fairness NW (DV), M2 = Team Work NW (DV), M3 = Want to work in team NW (DV), M4 = Distrust NW (DV)', caption.above = TRUE, digits = 3, leading.zero = F)

htmltools::HTML(h)
```
# Moderator Analysis: Representation 
```{r, error=FALSE, warning = FALSE, message = FALSE, results='hide'}

model_9<-lmer(fairness~nwhitefemale + whitemen + nwhitemen+ whitefemale+trial_condition + nwhitefemale:trial_condition + whitemen:trial_condition + nwhitemen:trial_condition + whitefemale:trial_condition + (1 | subject), data = data2)
summary(model_9)

model_10<-lmer(team_work~nwhitefemale + whitemen + nwhitemen+ whitefemale+trial_condition + nwhitefemale:trial_condition + whitemen:trial_condition + nwhitemen:trial_condition + whitefemale:trial_condition + (1 + trial_condition|subject), data = data2)
summary(model_10)

model_11<-lmer(work_in_team~nwhitefemale + whitemen + nwhitemen+ whitefemale+trial_condition + nwhitefemale:trial_condition + whitemen:trial_condition + nwhitemen:trial_condition + whitefemale:trial_condition + (1 + trial_condition|subject), data = data2)
summary(model_11)

model_12<-lmer(distrust~nwhitefemale + whitemen + nwhitemen+ whitefemale+trial_condition + nwhitefemale:trial_condition + whitemen:trial_condition + nwhitemen:trial_condition + whitefemale:trial_condition + (1 + trial_condition|subject), data = data2)
summary(model_12)

```
```{r}
h<-htmlreg(l = list(model_9, model_10, model_11, model_12), center = TRUE, stars = c(0.001, 0.01, 0.05), bold = 0.05, caption = 'M1 = Fairness NW (DV), M2 = Team Work NW (DV), M3 = Want to work in team NW (DV), M4 = Distrust NW (DV)', caption.above = TRUE, digits = 3, leading.zero = F)

htmltools::HTML(h)
```
# Moderator Analysis: SDO 
```{r, error=FALSE, warning = FALSE, message = FALSE, results='hide'}

model_13<-lmer(fairness~nwhitefemale + whitemen + nwhitemen+ whitefemale+SDO + nwhitefemale:SDO + whitemen:SDO + nwhitemen:SDO + whitefemale:SDO + (1 + SDO|subject), data = data2)
summary(model_13)

model_14<-lmer(team_work~nwhitefemale + whitemen + nwhitemen+ whitefemale+SDO + nwhitefemale:SDO + whitemen:SDO + nwhitemen:SDO + whitefemale:SDO + (1 + SDO|subject), data = data2)
summary(model_14)

model_15<-lmer(work_in_team~nwhitefemale + whitemen + nwhitemen+ whitefemale+SDO + nwhitefemale:SDO + whitemen:SDO + nwhitemen:SDO + whitefemale:SDO + (1 + SDO|subject), data = data2)
summary(model_15)

model_16<-lmer(distrust~nwhitefemale + whitemen + nwhitemen+ whitefemale+SDO + nwhitefemale:SDO + whitemen:SDO + nwhitemen:SDO + whitefemale:SDO + (1 + SDO|subject), data = data2)
summary(model_16)

```
```{r}
h<-htmlreg(l = list(model_13, model_14, model_15, model_16), center = TRUE, stars = c(0.001, 0.01, 0.05), bold = 0.05, caption = 'M1 = Fairness NW (DV), M2 = Team Work NW (DV), M3 = Want to work in team NW (DV), M4 = Distrust NW (DV)', caption.above = TRUE, digits = 3, leading.zero = F)

htmltools::HTML(h)
```

# Moderator Analysis: Political Orientation
```{r, error=FALSE, warning = FALSE, message = FALSE, results='hide'}

model_17<-lmer(fairness~nwhitefemale + whitemen + nwhitemen+ whitefemale+PoliticalOrientation + nwhitefemale:PoliticalOrientation + whitemen:PoliticalOrientation + nwhitemen:PoliticalOrientation + whitefemale:PoliticalOrientation + (1 + PoliticalOrientation|subject), data = data2)
summary(model_17)

model_18<-lmer(team_work~nwhitefemale + whitemen + nwhitemen+ whitefemale+PoliticalOrientation + nwhitefemale:PoliticalOrientation + whitemen:PoliticalOrientation + nwhitemen:PoliticalOrientation + whitefemale:PoliticalOrientation + (1 + PoliticalOrientation|subject), data = data2)
summary(model_18)

model_19<-lmer(work_in_team~nwhitefemale + whitemen + nwhitemen+ whitefemale+PoliticalOrientation + nwhitefemale:PoliticalOrientation + whitemen:PoliticalOrientation + nwhitemen:PoliticalOrientation + whitefemale:PoliticalOrientation + (1 + PoliticalOrientation|subject), data = data2)
summary(model_19)

model_20<-lmer(distrust~nwhitefemale + whitemen + nwhitemen+ whitefemale+PoliticalOrientation + nwhitefemale:PoliticalOrientation + whitemen:PoliticalOrientation + nwhitemen:PoliticalOrientation + whitefemale:PoliticalOrientation + (1 + PoliticalOrientation|subject), data = data2)
summary(model_20)

```
```{r}
h<-htmlreg(l = list(model_17, model_18, model_19, model_20), center = TRUE, stars = c(0.001, 0.01, 0.05), bold = 0.05, caption = 'M1 = Fairness NW (DV), M2 = Team Work NW (DV), M3 = Want to work in team NW (DV), M4 = Distrust NW (DV)', caption.above = TRUE, digits = 3, leading.zero = F)

htmltools::HTML(h)
```

# Moderator Analysis: BJW
```{r, error=FALSE, warning = FALSE, message = FALSE, results='hide'}

model_21<-lmer(fairness~nwhitefemale + whitemen + nwhitemen+ whitefemale+BJW + nwhitefemale:BJW + whitemen:BJW + nwhitemen:BJW + whitefemale:BJW + (1 + BJW|subject), data = data2)
summary(model_21)

model_22<-lmer(team_work~nwhitefemale + whitemen + nwhitemen+ whitefemale+BJW + nwhitefemale:BJW + whitemen:BJW + nwhitemen:BJW + whitefemale:BJW + (1 + BJW|subject), data = data2)
summary(model_22)

model_23<-lmer(work_in_team~nwhitefemale + whitemen + nwhitemen+ whitefemale+BJW + nwhitefemale:BJW + whitemen:BJW + nwhitemen:BJW + whitefemale:BJW + (1 + BJW|subject), data = data2)
summary(model_23)

model_24<-lmer(distrust~nwhitefemale + whitemen + nwhitemen+ whitefemale+BJW + nwhitefemale:BJW + whitemen:BJW + nwhitemen:BJW + whitefemale:BJW + (1 + BJW|subject), data = data2)
summary(model_24)

```
```{r}
h<-htmlreg(l = list(model_21, model_22, model_23, model_24), center = TRUE, stars = c(0.001, 0.01, 0.05), bold = 0.05, caption = 'M1 = Fairness NW (DV), M2 = Team Work NW (DV), M3 = Want to work in team NW (DV), M4 = Distrust NW (DV)', caption.above = TRUE, digits = 3, leading.zero = F)

htmltools::HTML(h)
```